Outline--Draft JCP format for: Reactive Force Field for Solid Oxides Containing Lanthanum

### 2019-06-01 Paper/paper.tex
Update paper.tex
Added La-EoS figure and discussion about it

@@

>>>>

\graphicspath{ {./images/} }

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=1]{three-La-eos.pdf}
\caption{Calculated equations of state corresponding to crystalline La in hexagonal (top), fcc (middle), and bcc (bottom) forms.}
\label{fig:laeos}
\end{figure}

The equations of state for the three forms of Lanthanum are presented in Fig.~\ref{fig:laeos}.
The plots show the parabolic behaviour of the equation of state, and that the parametrized ReaxFF can reproduce the results from DFT within an acceptable margin of error.
As for the trends in stability of the three phases, ReaxFF is unable to properly reproduce it.
The reported experimental trend places $\alpha$-La as the most stable, followed by $\gamma$-La, and then by$\beta$-La.
In the case of ReaxFF the trend goes from most stable to less stable as $\gamma$-La, $\beta$-La, and $\alpha$-La.
While the inability to reproduce stability is a known issue in ReaxFF, it is worth mentioning that in the case of La, the differences in energy between the phases is in the order of $\approx$~0.5~kcal/mol.
It is then unsurprising that the parametrized force field is unable to exactly reproduce the trend,  given how small the difference in energy is compared to the target error in the fitting of the force field, which averages around 5~kcal/mol.
